Neural and Symbolic Spatiotemporal Optimization of Cosmological Particel-Mesh Simulation

### 2023-02-07 docs/papers/sto/sto.tex
FIXUP draft: rm scaled histogram placeholder
FIXUP draft: add TODO

\section*{TODO}
\begin{itemize}
\item Be careful with the non-deterministic ICs generated on GPUs.
  \begin{enumerate}
  \item Saving them on disks and loading them during training solves
    this but may introduce IO or memory problem;
  \item Generating them on CPUs for training data and also training
    might suffice while requireing such data loader implementation;
  \item Generating them on GPUs for training data and training will
    introduce additional source of initial deviations to be nonlinearly
    amplified. There are flags that makes certain operations
    deterministic but slow on GPUs, but those are enviroment variables
    that function globally and cannot be applied locally only on the IC
    generation during training.
  \item Generating ICs and then train on GPUs with double precision and
    then compute the loss at single precision (Gadget4 should be run at
    double precision) should work, and likely be the simplest solution.
    But for this to work the final training loss should be much larger
    than the level of reproducibility.
  \end{enumerate}
\item Non-integer multiple mesh shapes: for uniform particle grid, test
  (with double precision on CPUs) whether they start moving by artifact
  forces on cell scales, in 3 cases: no deconvolution, with CIC
  deconvolution, with SO.
\item For TO, probably necessary to first incorporate Oliver Hahn's
  recent improvement on FastPM integrator arXiv:2301:09655.
\end{itemize}

@@

\begin{figure*}
  \centering
  %\includegraphics[width=0.8\linewidth]{name.ext}
  \caption{1D histogram of the parameters sampled with RQMC and scaled
  as in \autoref{tab:param}}.
  \label{fig:hist}
\end{figure*}

>>>>

\section*{TODO}
\begin{itemize}
\item Compare one pair of Gadget4 and \pmwd\ (with say 100 to 1000 time
    steps) results and make sure that they agree perfectly on the large
    scales. For this purpose the box size should be large enough (in
    linear regime), say 1 Gpc/$h$.
\item Be careful with the non-deterministic ICs generated on GPUs.
  \begin{enumerate}
  \item Saving them on disks and loading them during training solves
    this but may introduce IO or memory problem;
  \item Generating them on CPUs for training data and also training
    might suffice while requireing such data loader implementation;
  \item Generating them on GPUs for training data and training will
    introduce additional source of initial deviations to be nonlinearly
    amplified. There are flags that makes certain operations
    deterministic but slow on GPUs, but those are enviroment variables
    that function globally and cannot be applied locally only on the IC
    generation during training.
  \item Generating ICs and then train on GPUs with double precision and
    then compute the loss at single precision (Gadget4 should be run at
    double precision) should work, and likely be the simplest solution.
    But for this to work the final training loss should be much larger
    than the level of reproducibility.
  \end{enumerate}
\item Non-integer multiple mesh shapes: for uniform particle grid, test
  (with double precision on CPUs) whether they start moving by artifact
  forces on cell scales, in 3 cases: no deconvolution, with CIC
  deconvolution, with SO.
\item For TO, probably necessary to first incorporate Oliver Hahn's
  recent improvement on FastPM integrator arXiv:2301:09655.
\end{itemize}

@@
